Decentralised location proof system

### 2016-04-23 thesis/evaluation.tex
Adding final updates

The previous chapter introduced a model for a decentralised location proof system. This chapter will present an evaluation of the model with respect to the design goals defined in section \ref{sec:design_goals}.

@@

The sytem described in chapter \ref{ch:design} inherently satisfies this property of OTIT. Verifier nodes may be operated by banks, employers, or other parties who have a vested interest in allowing their customers or employees to be able to prove their location. These Verifiers can verify or reject a mobile nodes claimed location by examining the nodes chronological link of transactions (as shown in figure \ref{fig:tree}). The Verifier will recursively generate and examine this tree until it can conclude whether or not the transaction chain is valid.

@@

A \textit{sub-set} of size $m$ of a node $A$'s proof chain, beginning at proof $n$, contains all proofs in the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$. Every transaction in this chain is split into two parts, a transaction data and link data part, and separately encrypted. If a node reveals keys for a Verifier to decrypt all transactions in the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$, it will not be possible for the Verifier to discover transaction $ID_{A}[n-m-1]$, or any transaction outside the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$.

@@

In this system, the data is stored in a central blockchain that the Verifier has access to, and the user provides the Verifier  with decryption keys and indexes into just a sub-section of this data. Therefore the data sent to from the user to the Verifier, $KP_{An}$, is quite small in size.

The Verifier has the freedom to decide how comprehensively to investigate the users data; It can decide how far to recurse while investigating the tree of alibi relationships. This property of OTIT is therefore satisfied by allowing the Verifier to decide how complex the verification process needs to be.

\section{Threat analysis}
\subsection{False presence}
In a false presence attack, a dishonest user attempts to obtain a location proof for a false location.

In this system, any dishonest user attempting to obtain a false location proof with an honest alibi will not succeed, as the honest alibi will abort the exchange (see section \ref{ssec:aborting_exchanges}). A dishonest user who publishes a transaction onto the blockchain with a fabricated alibi will also not succeed, as the transaction will be rejected during verification if a Verifier can't find the matching alibi transaction. The system is therefore not vulnerable to a false presence attack.

\subsection{Malicious intruders}
A malicious intruder offers to help another user to prove a false location, but doesn't prove a false location for itself.

@@

Identity discovery is impossible by design in this system. By using a different, seemingly random identity for each transaction, it is impossible for a curious user to determine if two transactions belong to the same user or not. It is therefore impossible for a curious user to learn another user's identity by monitoring location proofs.

@@

@@

A weak identity attack will not affect this system. Exchanging public keys or identities between colluding users offers no advantage. This is because a Verifier will ensure that any users requesting verification own the private key corresponding to the public key transferred during the verification request (see section \ref{ssec:verification}).

@@

@@

If the proof has not been added to the blockchain yet, then it is possible for the malicious user to modify it to attempt to spoof a false location. However this attack will not work on this system. Any Verifier will reject the transaction on the grounds that it contains contradictory information to the alibis transaction, which has not been modified.

@@

Previous research \cite{sybil} has concluded that the only provably correct way of preventing a Sybil attack in a decentralised system is to use a \textit{centralised} name system to coordinate the distribution of identities. Therefore a Sybil attack vulnerability must be taken out of the scope of this system, as this system is focused on a decentralised approach to location verification.

>>>>

The previous chapter introduced a model for a decentralised location proof system. This chapter will present a case-based evaluation of the model with respect to the design goals defined in section \ref{sec:design_goals}.

In a case-based evaluation, the response of the system model to each \textit{case} (property or threat) is reasoned about. A conclusion is then reached as to the effectiveness of the model in satisfying or defending against each property-based or threat-based case, respectively. Evidence is shown in the form of logical arguments (reasoning) deriving from the definition of each case. This kind of evaluation contrasts a benchmark-based evaluation, where a system implementation is benchmarked against a test suite, because this system is a model rather than an implementation.

@@

The system described in chapter \ref{ch:design} inherently satisfies this property of OTIT. Verifier nodes may be operated by banks, employers, or other parties who have a vested interest in allowing their customers or employees to be able to prove their location. These Verifiers can verify or reject a mobile nodes claimed location by examining the nodes chronological link of transactions (as shown in figure \ref{fig:tree}). The Verifier will recursively generate and examine this tree until it can conclude whether or not the transaction chain is valid.

@@

A \textit{sub-set} of size $m$ of a node $A$'s proof chain, beginning at proof $n$, contains all proofs in the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$. Every transaction in this chain is split into two parts, a transaction data and link data part, which are separately encrypted. If a node reveals keys for a Verifier to decrypt all transactions in the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$, it will not be possible for the Verifier to discover transaction $ID_{A}[n-m-1]$, or any transaction outside the sequence $ID_{A}[n-m]$ to $ID_{A}[n]$.

@@

In this system, the data is stored in a central blockchain that the Verifier has access to. A user provides a Verifier  with decryption keys and indexes for a sub-section of this data. Therefore the data sent from the user to the Verifier, $KP_{An}$, is quite small in size.

Verifiers have the freedom to decide how comprehensively to investigate a user's data; They can decide how far to recurse while investigating the tree of alibi relationships. This property of OTIT is therefore satisfied by allowing Verifiers to decide how complex the verification process needs to be.

\section{Threat analysis}
Section \ref{ssec:threats} defined a number of threats being considered for this project, which were gathered from existing publications \cite{luo,khan}. The system presented in this project is evaluated against these threats below.

\subsection{False presence}
In a false presence attack, a dishonest user attempts to obtain a location proof for a false location.

In this system, any dishonest user attempting to obtain a false location proof with an honest alibi will not succeed, as the honest alibi will abort the exchange (see section \ref{ssec:aborting_exchanges}). A dishonest user who publishes a transaction onto the blockchain with a fabricated alibi will also not succeed, as the transaction will be rejected during verification if a Verifier cannot find the matching alibi transaction. The system is therefore not vulnerable to a false presence attack.

\subsection{Malicious intruders}
A malicious intruder offers to help another user to prove a false location, but does not prove a false location for itself.

@@

Identity discovery is impossible by design in this system. By using a different, seemingly random identity for each transaction, it is impossible for a curious user to determine if two transactions belong to the same user. It is therefore impossible for a curious user to learn another user's identity by monitoring location proofs.

@@

This result highlights another advantage of modeling a location proof system in a decentralised manner. Luo et al. \cite{luo}, in their model of a centralised location proof system, identified a wormhole attack as a vulnerability of their model, and removed it from scope. Due to the lack of a central authority to fool, the decentralised system proposed in this project is not vulnerable to a wormhole attack by design.

@@

A weak identity attack will not affect this system. Exchanging public keys or identities between colluding users offers no advantage, as this system does not use fixed identifiers to identify users, rather it uses a seemingly random identity generation technique, as explained in section \ref{sec:identities}. A user will exchange its constant (unchanging) public key when requesting verification, however, a Verifier will check that all requesting users own the private key corresponding to their claimed public key (see section \ref{ssec:verification}). Malicious users attempting a weak identity attack will be unable to spoof a valid private key, assuming the security of the underlying cryptography system.

Luo et al. \cite{luo} identified a weak identity attack as a further weakness in their model. The evaluation above shows that by using a technique for seemingly random identity generation, this system remains invulnerable to a weak identity attack, even in a decentralised setting.

@@

This is an especially interesting result. The publication that presented this threat case \cite{khan} identified a false assertion attack as a vulnerability in their system, and took it out of scope. This proves that in the case of false assertion, the decentralised model presented in this paper outperforms existing centralised models.

@@

If the proof has not been added to the blockchain yet, then it is possible for the malicious user to modify it to attempt to spoof a false location. However this attack will not work on this system. Any Verifier will reject the transaction on the grounds that it contains contradictory information to the alibi's transaction, which has not been modified.

@@

Previous research \cite{sybil} has concluded that the only provably correct way of preventing a Sybil attack in a decentralised system is to use a \textit{centralised} name system to coordinate the distribution of identities. Therefore a Sybil attack vulnerability must be taken out of the scope of this system, as this system is focused on a decentralised approach to location verification. However, a Sybil attack would have to be highly targeted in order to fool a Verifier into verifying a false location proof chain, due to multiple strong options of mitigation against such an attack.

\null
The evaluation presented in this chapter shows that despite the current vulnerability to a Sybil attack, this model is a viable design of a decentralised location proof system. This is especially interesting because the model was evaluated against cases used to evaluate centralised proof systems, outperforming them in certain cases.

### 2016-04-23 thesis/introduction.tex
Adding final updates

This project describes a decentralised location proof system that is capable of operating on \textit{mobile nodes} (mobile devices). I propose a design in which location proofs are obtained using other untrusted mobile nodes as \textit{alibis}. Proofs will be created as two mobile nodes communicate over an ad-hoc bluetooth network, transfer encrypted location information, and publish it on a public append-only bulletin board, known as a \textit{blockchain}. The decentralised nature of the system means that there is no single point of failure, no entity controlling the security of every node's location proofs, and no entity capable of violating another node's privacy. This is because in a decentralised system, no node is ``in charge'', and no node has more authority in the system than any other node.

@@

\subsection{Conclusion and Future Work}
Chapter 5 presents the conclusions of the project, and details interesting areas for possible future work relating to the project.

>>>>

This project describes a decentralised location proof system that is capable of operating on \textit{mobile nodes} (mobile devices), and is designed such that location proofs are obtained using other untrusted mobile nodes as \textit{alibis}. Proofs will be created as two mobile nodes communicate over an ad-hoc bluetooth network, transfer encrypted location information, and then publish it onto a public append-only bulletin board, known as a \textit{blockchain}. The decentralised nature of the system means that there is no single point of failure, no entity controlling the security of every node's location proofs, and no entity capable of violating another node's privacy. This is because in a decentralised system, all nodes have an equal level of authority.

Evaluation of the project is presented using case-based analysis. Desirable properties of location proof systems are identified from the state of the art, along with common threats (attacks) in such systems. These are known as cases. The model described in this project is then evaluated against each case, by means of reasoning. Based on analysis of the state of the art, this is standard practice in the evaluation of such systems.

@@

\subsection{Conclusion and future work}
Chapter 5 presents the conclusions of the project, and details interesting areas for possible future work relating to the project.

### 2016-04-23 thesis/thesis.tex
Adding final updates

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subcaption}

@@

\begin{document}
\pagenumbering{roman}
\maketitle

>>>>

\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{setspace}

@@

\begin{document}

\onehalfspacing

\pagenumbering{roman}
\maketitle

\renewcommand{\abstractname}{Abstract}
\begin{abstract}
Location proof systems are systems which allow a user to undeniably prove its location to another user. Existing systems have thus far been designed in a centralised manner, using a trusted central server to provide honest location proofs to users. This presents privacy and reliability issues, as these systems rely on the honesty and availability of the central server. This report presents the design and evaluation of a decentralised location proof system, which overcomes the shortcomings of existing centralised location proof systems.
\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
I wish to thank my supervisor Stephen Barrett, for his continuous guidance and enthusiasm throughout this project. I would also like to thank Michael Clear for his excellent advice and suggestions, and Douglas Temple for his generous support.
\end{abstract}
